### 2016-07-14 ch02-qlogms/excitation-design.tex
Assumptions + some references

\begin{assumption}
The resonance frequencies $\wn[i]$ of all the sub-systems in \eqref{eq:excitation:PFE} are well-separated in the frequency domain such that there is little modal overlap, i.e. $\modalOverlap \ll 1$.
\end{assumption}

@@

\begin{remark}
The modal overlap $\modalOverlap$ is given~\citep{Ege2009} as the ratio of the average $3\unit{dB}$ bandwidth to the average difference in resonance frequencies for all resonances in the frequency band of interest.
Often, the modal overlap is linked to the model density $\modalOverlap(\omega) = \wdB \modalDensity{\omega}$.
In acoustic and structural engineering, expressions exist for the theoretical modal density $\modalDensity{f}$ in specific geometries such as beams, plates, square volumes~\citep{Hart1971,Bies2009}.
Specifically, beams exhibit a modal density $\modalDensity{\omega} = \bigO{\omega^{-1/2}}$, for plates this becomes $\modalDensity{\omega} = \bigO{1}$, and for volumes $\modalDensity{\omega} = \bigO{\omega}$.
As such, the previous assumption practically limits the use of the excitation signals to beams or the low-frequency region of plates and volumes~\citep{Ege2009}.
\end{remark}

@@

  \begin{property}\label{prop:excitation:log:relBW}
   Each frequency band $B = \ClosedInterval{f, \kappa f}$ with $\kappa \in \PositiveRealNumbers \without \set{0,1}$ that is completely within the range of the excited logarithmic grid of frequencies $\set{f_1, \ldots, f_F}$ contains a constant number of frequency lines
   \begin{equation}
     F_{B} \isdef
     \floor{\frac{\log (\kappa f) - \log( f )}{\log \alpha}}
         = \floor{\log_{\alpha} \kappa}
         \text{.}
   \end{equation}
   \end{property}
  \begin{example}
    For the frequency decade band $\decade(f) \isdef \ClosedInterval{f, 10 f}$, a logarithmic frequency grid contains $F_{\decade} = \floor{\log_{\alpha} 10}$ excited lines.
    Note that this is independent of the frequency $f$.
  \end{example}
  \begin{remark}
    In different contexts, e.g. electrical circuit simulators such as \gls{SPICE}~\citep{Kundert1995}, measurement equipment such as \glspl{DSA} and programming languages, it is more common to specify the spacing of a logarithmic grid using the total number of frequencies ($F$) or the number of frequencies per decade ($F_{\decade}$) instead of the grid ratio $\alpha$.
    Obviously, such alternate specifications are equivalent.
  \end{remark}
  \begin{example} \label{eg:excitation:logarithmicGrid:matlab}
    The \MATLAB code \mcode[mathescape]{f = logspace(log10($f_{\min}$), log10($f_{\max}$), $F$)} produces a logarithmically spaced frequency vector \mcode{f} with $F$ elements in the range $\left[ f_{\min}, f_{\max} \right]$.
    As such, the effective frequency ratio $\alpha = \sqrt[F]{\frac{f_{\max}}{f_{\min}}}$ in this vector.
  \end{example}
  \begin{example}
    The~\citet{HP3562A} has a logarithmic measurement mode that ensures that each decade is covered by $F_{\decade} = 80$ lines~ to measure an \gls{FRF}.
    %TODO: make sure "\gls{FRF}" has already been used before this point
    This is equivalent to a grid spacing $\alpha = \sqrt[80]{10} \approx 1.029$.
  \end{example}

@@

   The free parameters $(\dc, \damping, \wn, \wz)$ of the sub-system are reduced to only $(\damping, \wn)$ and the others are fixed during our experiments: $\dc = 1$ and $\wz \to \infty$. 
   \begin{remark}
   Implicitly, this considers a design where each of the sub-systems have an equal gain $\dc=1$ and residue $\wz \to\infty$.
   In practice, this is often not a reasonable assumption, but the design can be adapted in a straightforward manner.
   Concretely, using a first experiment with the proposed signal, one can estimate the different parameters of the sub-systems and optimize the amplitude spectrum of the signal to take those into account: for sub-systems where $\dc$ is lower than on average, the amplitude spectrum needs to be increased near the resonance frequency and \latin{vice versa}.
   \end{remark}

>>>>

\begin{assumption}
The resonance frequencies $\wn[i]$ of all the sub-systems in \eqref{eq:excitation:PFE} are well-separated in the frequency domain:
\begin{equation}
  \forall i,j \in \NaturalNumbers, i \neq j : \abs{\wn[i] - \wn[j]} >  \frac{\BW_i + \BW_j}{2},
\end{equation}
where $\BW_{i} \approx 2 \damping[i]\wn[i]$ denotes the $3\unit{dB}$ bandwidth of the $i^{\text{th}}$ resonant sub-system. 
\end{assumption}

\begin{remark}
The aforementioned assumption practically implies that there is no overlap between different resonances and hence there is little so-called `modal overlap'.
The modal overlap $\modalOverlap$ is given~\citep{Ege2009} as the ratio of the average $3\unit{dB}$ bandwidth to the average difference in resonance frequencies for all resonances in the frequency band of interest.
Often, the modal overlap is linked to the model density $\modalOverlap(\omega) = \wdB \modalDensity{\omega}$.
In acoustic and structural engineering, expressions exist for the theoretical modal density $\modalDensity{f}$ in specific geometries such as beams, plates, square volumes~\citep{Hart1971,Bies2009}.
Specifically, beams exhibit a modal density $\modalDensity{\omega} = \bigO{\omega^{-1/2}}$, for plates this becomes $\modalDensity{\omega} = \bigO{1}$, and for volumes $\modalDensity{\omega} = \bigO{\omega}$.
As such, the previous assumption practically limits the use of the excitation signals to beams or the low-frequency region of plates and volumes~\citep{Ege2009}.
\end{remark}

@@

@@

  \begin{property}\label{prop:excitation:log:relBW}
   Each frequency band $B = \ClosedInterval{f, \kappa f}$ with $\kappa \in \PositiveRealNumbers \without \set{0,1}$ that is completely within the range of the excited logarithmic grid of frequencies $\set{f_1, \ldots, f_F}$ contains a constant number of frequency lines
   \begin{equation}
     F_{B} \isdef
     \floor{\frac{\log (\kappa f) - \log( f )}{\log \alpha}}
         = \floor{\log_{\alpha} \kappa}
         \text{.}
   \end{equation}
   \end{property}
  \begin{example}
    For the frequency decade band $\decade(f) \isdef \ClosedInterval{f, 10 f}$, a logarithmic frequency grid contains $F_{\decade} = \floor{\log_{\alpha} 10}$ excited lines.
    Note that this is independent of the frequency $f$.
  \end{example}
  \begin{remark}
    In different contexts, e.g. electrical circuit simulators such as \gls{SPICE}~\citep{Kundert1995}, measurement equipment such as \glspl{DSA} and programming languages, it is more common to specify the spacing of a logarithmic grid using the total number of frequencies ($F$) or the number of frequencies per decade ($F_{\decade}$) instead of the grid ratio $\alpha$.
    Obviously, such alternate specifications are equivalent.
  \end{remark}
  \begin{example} \label{eg:excitation:logarithmicGrid:matlab}
    The \MATLAB code \mcode[mathescape]{f = logspace(log10($f_{\min}$), log10($f_{\max}$), $F$)} produces a logarithmically spaced frequency vector \mcode{f} with $F$ elements in the range $\left[ f_{\min}, f_{\max} \right]$.
    As such, the effective frequency ratio $\alpha = \sqrt[F]{\frac{f_{\max}}{f_{\min}}}$ in this vector.
  \end{example}
  \begin{example}
    The~\citet{HP3562A} has a logarithmic measurement mode that ensures that each decade is covered by $F_{\decade} = 80$ lines~ to measure an \gls{FRF}.
    This is equivalent to a grid spacing $\alpha = \sqrt[80]{10} \approx 1.029$.
  \end{example}

@@

   The free parameters $(\dc, \damping, \wn, \wz)$ of the sub-system are reduced to only $(\damping, \wn)$ and the others are fixed during our experiments: $\dc = 1$ and $\wz \to \infty$. 
   \begin{remark}
   Implicitly, this considers a design where each of the sub-systems have an equal gain $\dc=1$ and residue $\wz \to\infty$.
   In practice, this is often not a reasonable assumption, but the design can be adapted in a straightforward manner.
   Concretely, using a first experiment with the proposed signal, one can estimate the different gains of the sub-systems and optimize the amplitude spectrum of the signal to take those into account: for sub-systems where $\dc$ is lower than on average, the amplitude spectrum needs to be increased near the resonance frequency and \latin{vice versa}.
   \end{remark}

### 2016-07-14 ch05-initvals/initial-values.tex
Assumptions + some references

Parametric identification of \gls{LTI} systems from either input/output data or non-parametric frequency response data, has been well developed as evidenced by published literature~\citep{Pintelon2012,Ljung1999,Schoukens1999,Pintelon1998,Soderstrom1989,Goodwin1977,Brillinger1981,Sanathanan1963,McKelvey2002}.
Many of such parametric identification algorithms, however, require solving non-linear or non-convex optimization problems.
This often involves an iterative algorithm to produce the optimal model.
 The resulting model, however, depends on which initial estimates are used to start up the optimization process: typically one can end up in local minima, leading to models of sub-optimal quality.
 Hence, good initial estimates are essential to obtain a high quality model estimate.
 In this chapter, the \gls{MLE} is used as a proxy for any parametric transfer function estimator, since the \gls{MLE} is commonly used and has desirable properties such as efficiency and consistency.
 Numerous other parametric identification techniques are devoted to the development of parametric plants $G(q^{-1},\theta)$ and parametric noise models  $H(q^{-1},\theta)$, where  $\theta$ is the model parameters vector \citep{Ljung1999,Soderstrom1989,Pintelon2012}.
 Since the initial value generation methods are not specifically tailored towards the \gls{MLE}, other parametric identification frameworks are likely to benefit from these improved starting values as well.
 Hence, the presented approach is complementary to initialization schemes such as the work of~\citet{vanHerpen2014} that focuses on improving the optimization algorithm, rather than the starting values.

>>>>

Parametric identification of \gls{LTI} systems from either input/output data or non-parametric frequency response data, has been well developed as evidenced by published literature~\citep{Pintelon2012,Ljung1999,Schoukens1999,Pintelon1998,Soderstrom1989,Goodwin1977,Brillinger1981,Sanathanan1963,McKelvey2002,Peeters2004}.
Many of such parametric identification algorithms, however, require solving non-linear or non-convex optimization problems.
This often involves an iterative algorithm to produce the optimal model.
 The resulting model, however, depends on which initial estimates are used to start up the optimization process: typically one can end up in local minima, leading to models of sub-optimal quality.
 Hence, good initial estimates are essential to obtain a high quality model estimate.
 In this chapter, the \gls{MLE} is used as a proxy for any parametric transfer function estimator, since the \gls{MLE} is commonly used and has desirable properties such as efficiency and consistency.
 Numerous other parametric identification techniques are devoted to the development of parametric plants $G(q^{-1},\theta)$ and parametric noise models  $H(q^{-1},\theta)$, where  $\theta$ is the model parameters vector \citep{Ljung1999,Soderstrom1989,Pintelon2012}.
 Since the initial value generation methods are not specifically tailored towards the \gls{MLE}, other parametric identification frameworks are likely to benefit from these improved starting values as well.
 Hence, the presented approach is complementary to initialization schemes such as the work of~\citet{vanHerpen2014} that focuses on improving the optimization algorithm, rather than the starting values.
